On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-09-29 paper/paper.tex
Remove comparison to SSA

In this paper, a C backend is given as an example. The Core plugin will
translate a subset of Haskell to the EDSL we have specified. The C backend will
then take expressions written in this EDSL and translate them to C code. This C
code can be compiled by a standard C compiler. In effect, the subset of Haskell
represented in the EDSL is compiled to C.

@@

A C backend is described in this paper. However, other backends could be constructed,
targeting different architectures.

@@

This backend is based on a globally unique name generator. A new C variable is created for each Haskell subexpression.
The result appears similar to static single assignment (SSA) form~\cite{Rosen:1988:SSA}.
It differs from SSA, however, in that these variables can be assigned multiple
times. In particular, a variable can be assigned in multiple branches of
an \ttt{if} statement or inside of a \ttt{while} loop. This simplifies
the implementation, as $\phi$ nodes are not needed.

>>>>

In this paper, a C backend is given as an example in Section \ref{sec:CBackend}. The Core plugin will
translate a subset of Haskell to the EDSL we have specified. The C backend will
then take expressions written in this EDSL and translate them to C code. This C
code can be compiled by a standard C compiler. In effect, the subset of Haskell
represented in the EDSL is compiled to C.

@@

A C backend is described in Section \ref{sec:CBackend}. However, other backends
could be constructed, targeting different architectures.

@@
